Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2016-02-08 IEEE TSP - Incl Bios/Report/convergence_distributed.tex
updated TSP submission

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using the following properties. (i) The feasible set is non-empty and bounded. Therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to the strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop. 8.2.6]{bertsekas2003convex} by using a diminishing step size in each subgradient update.}

Now, to show the convergence of \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that of \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and the \ac{ADMM} methods are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the whole sequence of iterates generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}

>>>>

Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using the following properties. (i) The feasible set is non-empty and bounded. Therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to the strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop. 8.2.6]{bertsekas2003convex} by using a diminishing step size in each subgradient update.

Now, to show the convergence of \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that of \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and the \ac{ADMM} methods are allowed to converge to the centralized solution in each \ac{SCA} step, then every limit point of the whole sequence of iterates generated by the distributed algorithms is a stationary point of \eqref{con} by following the discussions in Appendix \ref{sec-3.5}.

### 2016-02-08 IEEE TSP - Incl Bios/Report/dual_approach.tex
updated TSP submission

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are carried out until convergence or for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, it is still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange between the coupling \acp{BS}, the distributed schemes are often iterated for a limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step. We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.}

>>>>

Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are carried out until convergence or for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, it is still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange between the coupling \acp{BS}, the distributed schemes are often iterated for a limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step. We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.

### 2016-02-08 IEEE TSP - Incl Bios/Report/kkt_mse_approach.tex
updated TSP submission

In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements. We consider an idealized \ac{TDD} system due to the knowledge of local \ac{CSI} at the transmitter that includes channel between \ac{BS} \eqn{b} and all interfering users in the system. Similar work has been considered for the \ac{WSRM} problem with minimum guaranteed rate constraints in \cite{kaleva2013decentralized}. Since the work in \cite{kaleva2013decentralized} is similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint as in \eqref{eqn-3.1.4}, the formulation in \cite{kaleva2013decentralized} require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

However, in the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints. However, due to the non-differentiability of objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables. In order to make the objective function differentiable, we consider the following two conditions in which the absolute operator can be ignored without affecting the problem, namely,
\begin{itemize}
\item when the exponent \me{q} is even, or
\item when the number of backlogged packets waiting to be transmitted for each user is large enough, \textit{i.e}, \me{\textstyle Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator in the objective and queues in the first place as well.
\end{itemize}

@@

Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4}. At iteration \eqn{i}, the dual variables \me{\alpha^{(i)}} is a point in the line segment between \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} determined by using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}. The choice of \eqn{\rho^{(i)}}, which depends on the system, affects the convergence behavior and also controls the oscillations in the users' rate when \me{\sigma^{(i)}} is negative (before projection) due to over-allocation. However, in all numerical simulations, the step size \me{\rho^{(i)}} is fixed to \me{0.1} irrespectively.

@@

To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which embeds the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling. We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows. Upon receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user will evaluate the \ac{MMSE} receiver \eqref{kkt-mse-4.6} and notify to all \acp{BS} by using precoded uplink pilots. On receiving the pilots, each \ac{BS} updates the \ac{MSE} in \eqref{mse-error} as 
\begin{equation}
\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}.
\end{equation}
Using \eqn{\epsilon_{l,k,n}^{(i)}}, the variables \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are updated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} respectively, and the obtained dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration. The \ac{SCA} operating point is also updated with the current \ac{MSE} value.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{until convergence or \me{i \geq I_{\max}}}{
			update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform precoded downlink pilot transmission \;
			find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
			evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
			using precoded uplink pilots, \me{\mvec{w}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
			\me{i = i + 1} \;
		}
	}
	\caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
	\label{algo-4}
\end{algorithm}

>>>>

In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements. We consider an idealized \ac{TDD} system due to the knowledge of local \ac{CSI} at the transmitter that includes channel between \ac{BS} \eqn{b} and all interfering users in the system. Similar work has been considered for the \ac{WSRM} problem with minimum guaranteed rate constraints in \cite{kaleva2013decentralized}. However, in the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints. However, due to the non-differentiability of objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables. In order to make the objective function differentiable, we consider the following two conditions in which the absolute operator can be ignored without affecting the problem, namely,
\begin{itemize}
\item when the exponent \me{q} is even, or
\item when the number of backlogged packets waiting to be transmitted for each user is large enough, \textit{i.e}, \me{\textstyle Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator in the objective and queues in the first place as well.
\end{itemize}

@@

Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4.2}. At iteration \eqn{i}, the dual variable \me{\alpha^{(i)}} is a point in the line segment between \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} determined by using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}. The choice of \eqn{\rho^{(i)}}, which depends on the system, affects the convergence behavior and also controls the oscillations in the users' rate when \me{\sigma^{(i)}} is negative (before projection) due to over-allocation. However, in all numerical simulations, the step size \me{\rho^{(i)}} is fixed to \me{0.1} irrespectively.

@@

To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which embeds the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling. We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows. Upon receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user will evaluate the \ac{MMSE} receiver \eqref{kkt-mse-4.6} and notify to all \acp{BS} by using precoded uplink pilots. On receiving the pilots, each \ac{BS} updates the \ac{MSE} in \eqref{mse-error} as 
\begin{equation}
\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}.
\end{equation}
Using \eqn{\epsilon_{l,k,n}^{(i)}}, the variables \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are updated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} respectively, and the obtained dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration. The \ac{SCA} operating point is also updated with the current \ac{MSE} value.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l,k,n}}
	\KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{until convergence or \me{i \geq I_{\max}}}{
			update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform precoded downlink pilot transmission \;
			find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
			evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
			using precoded uplink pilots, \me{\mvec{w}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
			\me{i = i + 1} \;
		}
	}
	\caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
	\label{algo-4}
\end{algorithm}

### 2016-02-08 IEEE TSP - Incl Bios/Report/manuscript.tex
updated TSP submission

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic}

\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
\DeclareGraphicsExtensions{.eps}

@@

\ifCLASSINFOpdf
\epstopdfsetup{update,prepend,prefersuffix=false,suffix=}
\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
\pdfcompresslevel=9
\fi

\input{shortcuts}
\input{acronyms}

\newtoggle{includereview}
\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\togglefalse{single_column}
\togglefalse{enable_dist_fig}

\iftoggle{single_column}{
	\doublespacing
}

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Innovation (Tekes), Nokia Networks, Xilinx, Elektrobit and the Academy of Finland. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Senior Member,~IEEE}, Markku Juntti \IEEEmembership{Senior Member,~IEEE}, and Le-Nam Tran \IEEEmembership{Member,~IEEE}}\thanks{
	G. Venkatraman, A. T\"{o}lli and M. Juntti are with Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{L.-N. Tran was with Centre for Wireless Communications (CWC), Oulu, FI-90014. He is now with the Department of Electronic Engineering, Maynooth University, Maynooth, Co. Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie)}}

@@

\begin{IEEEkeywords}
Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \acs{WSRM}.
\end{IEEEkeywords}

@@

>>>>

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic,placeins}

\graphicspath{{./../Figures/}{./../Bios/}}
\DeclareGraphicsExtensions{.pdf}

@@

\input{shortcuts}
\input{acronyms}
\newtoggle{single_column}
\togglefalse{single_column}

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Innovation (Tekes), Nokia Networks, Xilinx, Elektrobit, the Riitta ja Jorma Takanen Foundation, and the Academy of Finland. This work was supported by a research grant from Science Foundation Ireland and is co-funded by the European Regional Development Fund under Grant 13/RC/2077. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Senior Member,~IEEE}, Markku Juntti \IEEEmembership{Senior Member,~IEEE}, and Le-Nam Tran \IEEEmembership{Member,~IEEE}}\thanks{
	G. Venkatraman, A. T\"{o}lli and M. Juntti are with Department of Communications Engineering (DCE), Centre for Wireless Communications (CWC), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{L.-N. Tran is with the Department of Electronic Engineering, Maynooth University, Maynooth, Co. Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie).}}

@@

\begin{IEEEkeywords}
\ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \acs{WSRM}, nonconvex problem, convergence analysis.
\end{IEEEkeywords}

@@

%\input{biography}

### 2016-02-08 IEEE TSP - Incl Bios/Report/queue_minimizing_intro.tex
updated TSP submission

% To begin with, we discuss the existing solution and its extension to solve the problem of resource allocation over multiple sub-channels. Then, we provide two approaches to solve the \ac{JSFRA} precoder design problem to minimize the total number of backlogged packets. At the end, we discuss a low complex solution for the \ac{JSFRA} problem by limiting the precoder design over each sub-channel at a given instant.
In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to its nonconvex nature. In addition, the objective of minimizing the number of the queued packets over space-frequency dimensions adds further complexity. Since the scheduling of users in each sub-channel is achieved by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling. Before discussing the proposed solutions, we consider the existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.

>>>>

% To begin with, we discuss the existing solution and its extension to solve the problem of resource allocation over multiple sub-channels. Then, we provide two approaches to solve the \ac{JSFRA} precoder design problem to minimize the total number of backlogged packets. At the end, we discuss a low complex solution for the \ac{JSFRA} problem by limiting the precoder design over each sub-channel at a given instant.
In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to its nonconvex nature. In addition, the objective of minimizing the number of the queued packets over space-frequency dimensions adds further complexity. Since the scheduling of users in each sub-channel is achieved by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling. Before discussing the proposed solutions, we consider an existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.
